Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-04-10 ident_manu.Rnw
submitted to ecomod

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{\Sexpr{vers}}

@@

\linenumbers
\acresetall

@@

\section{Methods}

@@

@@

% model schematic
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figs/mod_schem.pdf}
\caption{Conceptual representation of biogeochemical components modelled in \ac{cgem} (complete equations \citealt{Eldridge10}). FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
\label{fig:mod_schem}
\end{figure}

@@

<<areachg, eval = T, fig.cap = 'Estimated hypoxic area and monthly averages (km$^2 \\times$ 1000) using the default parameter settings (a, b) and the differences using a 50\\% increase in each parameter (c, d).  The selected parameters were the top sensitive in each parameter category for \\ac{do} in \\cref{fig:sensalltile,tab:dosens}. Error bars are 95\\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.  Areal extent of estimated hypoxia on August 28\\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = "\\textwidth">>=
# ##
# # area time series
# areats <- read_excel('ignore/runcompare.xlsx', sheet = 'area')
# 
# ##
# # get all arrays of hypox area for each parameter
# shts <- excel_sheets('ignore/runcompare.xlsx') %>% 
#   grep('array', ., value = T)
# latlon <- read_excel('ignore/runcompare.xlsx', sheet = 'Latlon') %>% 
#   list(
#     lat = c(.[,1])[[1]], 
#     lon = as.numeric(names(.)[-1])
#     ) %>% 
#   .[c('lat', 'lon')]
# 
# ls <- vector('list', length = length(shts))
# names(ls) <- shts
# for(sht in shts){
#  
#   cat(sht, '\t')
#   
#   # read the sheet, interpolate for higher res
#   tmp <- read_excel('ignore/runcompare.xlsx', sheet = sht, na = '-9999', col_names = F) 
#   tmp <- tmp[1:176,1:320] %>% 
#     as.matrix
#   obs <- list(x = latlon$lat, y = latlon$lon, z = tmp)
#   newgrd <- expand.grid(
#       x = approx(latlon$lat, n = 4 * ncol(tmp))$y,
#       y = approx(latlon$lon, n = 4 * nrow(tmp))$y
#       )
#   int_val <- fields::interp.surface(
#     obj = obs,
#     loc = newgrd
#     )
#   tmp <- data.frame(newgrd, tmp = int_val) %>%
#     spread(x, tmp) %>%
#     dplyr::select(-y) %>%
#     as.matrix %>% 
#     .[, ncol(.):1] %>% 
#     t
#   
#   # subset hypoxic areas, make polygon
#   # get only the large areas
#   tmp[tmp >= 64] <- NA
#   tmp[!is.na(tmp)] <- 1
#   tmp <- raster(tmp, 
#     xmn = min(latlon$lon), 
#     xmx = max(latlon$lon),   
#     ymn = min(latlon$lat), 
#     ymx = max(latlon$lat)
#     )
#   tmp <- rasterToPolygons(tmp, dissolve = T) %>% 
#     disaggregate
#   areas <- transform(data.frame(tmp), area = gArea(tmp, byid = T))
#   filt <- with(areas, which(area > 0.12)) #quantile(area, 0.99)))
#   tmp <- tmp[filt, ] %>% 
#     fortify
#   
#   ls[[sht]] <- data.frame(parm = sht, tmp)
#    
# }
# 
# # combine output from each sheet
# arrs <- do.call('rbind', ls) %>% 
#   mutate(
#     parm = gsub('_array$', '', parm)
#     ) %>% 
#   # filter(lat > 28) %>% 
#   tibble::remove_rownames(.) %>% 
#   unite('grp', parm, group, remove = F)
# 
# # save
# save(areats, arrs, file = 'data/area.RData', compress = 'xz')

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{\Sexpr{vers}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}

@@

% \linenumbers
\acresetall

@@

\section{Materials and Methods}

@@

\section*{Acknowledgments}

We thank the research staff of the USEPA Gulf Ecology Division, Environmental Modeling and Visualization Laboratory, and Naval Research Laboratory for their efforts developing the hydrodynamic and biogeochemical components of \ac{cgem}.

\section*{Role of Funding Sources}

This study was funded, reviewed, and approved for publication by the US EPA, National Health and Environmental Effects Research Laboratory.  However, the views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the US EPA.

@@

% model schematic
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figs/mod_schem.pdf}
\caption{Conceptual representation of biogeochemical components modelled in \ac{cgem} (complete equations in \citealt{Eldridge10}). FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
\label{fig:mod_schem}
\end{figure}

@@

<<areachg, eval = T, fig.cap = 'Estimated hypoxic area and monthly averages (km$^2 \\times$ 1000) using the default parameter settings (a, b) and the differences using a 50\\% increase in each parameter (c, d).  The selected parameters were the top sensitive in each parameter category for \\ac{do} in \\cref{fig:sensalltile,tab:dosens}. Error bars are 95\\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.  Areal extent of estimated hypoxia on August 28\\textsuperscript{th} using the default parameters (grey) and estimated changes with parameter perturbations is shown in (e).', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = "\\textwidth">>=
# ##
# # area time series
# areats <- read_excel('ignore/runcompare.xlsx', sheet = 'area')
# 
# ##
# # get all arrays of hypox area for each parameter
# shts <- excel_sheets('ignore/runcompare.xlsx') %>% 
#   grep('array', ., value = T)
# latlon <- read_excel('ignore/runcompare.xlsx', sheet = 'Latlon') %>% 
#   list(
#     lat = c(.[,1])[[1]], 
#     lon = as.numeric(names(.)[-1])
#     ) %>% 
#   .[c('lat', 'lon')]
# 
# ls <- vector('list', length = length(shts))
# names(ls) <- shts
# for(sht in shts){
#  
#   cat(sht, '\t')
#   
#   # read the sheet, interpolate for higher res
#   tmp <- read_excel('ignore/runcompare.xlsx', sheet = sht, na = '-9999', col_names = F) 
#   tmp <- tmp[1:176,1:320] %>% 
#     as.matrix
#   obs <- list(x = latlon$lat, y = latlon$lon, z = tmp)
#   newgrd <- expand.grid(
#       x = approx(latlon$lat, n = 4 * ncol(tmp))$y,
#       y = approx(latlon$lon, n = 4 * nrow(tmp))$y
#       )
#   int_val <- fields::interp.surface(
#     obj = obs,
#     loc = newgrd
#     )
#   tmp <- data.frame(newgrd, tmp = int_val) %>%
#     spread(x, tmp) %>%
#     dplyr::select(-y) %>%
#     as.matrix %>% 
#     .[, ncol(.):1] %>% 
#     t
#   
#   # subset hypoxic areas, make polygon
#   # get only the large areas
#   tmp[tmp >= 64] <- NA
#   tmp[!is.na(tmp)] <- 1
#   tmp <- raster(tmp, 
#     xmn = min(latlon$lon), 
#     xmx = max(latlon$lon),   
#     ymn = min(latlon$lat), 
#     ymx = max(latlon$lat)
#     )
#   tmp <- rasterToPolygons(tmp, dissolve = T) %>% 
#     disaggregate
#   areas <- transform(data.frame(tmp), area = gArea(tmp, byid = T))
#   filt <- with(areas, which(area > 0.12)) #quantile(area, 0.99)))
#   tmp <- tmp[filt, ] %>% 
#     fortify
#   
#   ls[[sht]] <- data.frame(parm = sht, tmp)
#    
# }
# 
# # combine output from each sheet
# arrs <- do.call('rbind', ls) %>% 
#   mutate(
#     parm = gsub('_array$', '', parm)
#     ) %>% 
#   # filter(lat > 28) %>% 
#   tibble::remove_rownames(.) %>% 
#   unite('grp', parm, group, remove = F)
# 
# # save
# save(areats, arrs, file = 'data/area.RData', compress = 'xz')

### 2017-04-10 ident_manu.tex
submitted to ecomod

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Sun Apr 9 11:59:44 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/452af951d19edb6129949898f5923b6e48c0ff26}{452af951d19edb6129949898f5923b6e48c0ff26}}

@@

\caption{Estimated hypoxic area and monthly averages (km$^2 \times$ 1000) using the default parameter settings (a, b) and the differences using a 50\% increase in each parameter (c, d).  The selected parameters were the top sensitive in each parameter category for \ac{do} in \cref{fig:sensalltile,tab:dosens}. Error bars are 95\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.  Areal extent of estimated hypoxia on August 28\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).}\label{fig:areachg}
\end{figure}

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Mon Apr 10 12:57:29 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/cb605034ebf62786fb3f412f99538ccdf606ffa4}{cb605034ebf62786fb3f412f99538ccdf606ffa4}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}

@@

\caption{Estimated hypoxic area and monthly averages (km$^2 \times$ 1000) using the default parameter settings (a, b) and the differences using a 50\% increase in each parameter (c, d).  The selected parameters were the top sensitive in each parameter category for \ac{do} in \cref{fig:sensalltile,tab:dosens}. Error bars are 95\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.  Areal extent of estimated hypoxia on August 28\textsuperscript{th} using the default parameters (grey) and estimated changes with parameter perturbations is shown in (e).}\label{fig:areachg}
\end{figure}
